MINOS Handover Plots

### 2024-10-21 minos/validation/handovers.Rmd
adding ncigs back into handovers

```{r}
# Read raw datafiles in
#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
# out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)

# base.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction',
#                                     drop.dead = TRUE,
#                                     drop.zero.weight = TRUE)

#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```

@@

## Income Quintile

```{r}
raw.dat <- raw.dat %>%
  group_by(time) %>%
  mutate(income_quint = ntile(hh_income, 5))

base.dat <- base.dat %>%
  group_by(time) %>%
  mutate(income_quint = ntile(hh_income, 5))
```

@@

```{r}
raw.maxAge <- raw.dat %>%
  group_by(time) %>%
  summarise(max_age = max(age)) %>%
  mutate(scen = 'final_US')

base.maxAge <- base.dat %>%
  group_by(time) %>%
  summarise(max_age = max(age)) %>%
  mutate(scen = 'baseline')

combined <- rbind(raw.maxAge, base.maxAge)

#handover_lineplots(raw.maxAge, base.maxAge, 'max_age')
ggplot(combined, aes(x = time, y = max_age, group = scen, colour = scen)) +
  geom_line() +
  geom_vline(xintercept = start.year, linetype = 'dashed') +
  labs(title = 'Max year of age') +
  xlab('Year') +
  ylab('Age')

@@

```{r}
raw.alive <- raw.dat %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(scen = 'final_US')

base.alive <- base.dat %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(scen = 'baseline')

#handover_boxplots(raw.alive, base.alive, 'n')
#handover_lineplots(raw.alive, base.alive, "n")

combined <- rbind(raw.alive, base.alive)

ggplot(combined, aes(x = time, y = n, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_vline(xintercept = start.year, linetype = 'dashed') +
  labs(title = 'Total Count in Sample') +
  xlab('Year') +
  ylab('Count')

@@

```{r}
# # Step 1: Filter for households with children
# households_with_kids <- raw.dat %>%
#   filter(nkids > 0) %>%
#   select(hidp, time, hh_income) %>%
#   distinct() %>%
#   select(-hidp)
# 
# # Step 2: Calculate income quintiles
# households_with_kids <- households_with_kids %>%
#   group_by(time) %>%
#   mutate(income_quintile = ntile(hh_income, 5)) %>%
#   ungroup()
# 
# # Step 3: Count households within each income quintile per year
# household_count_by_income_quintile <- households_with_kids %>%
#   group_by(time, income_quintile) %>%
#   summarise(n = n())
# 
# household_count_by_income_quintile
```

### Households With Children (Ethnic Group)

```{r}
raw.hhs_kids.ethnicity <- raw.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  group_by(time, ethnicity) %>%
  summarise(n = n(), .groups = 'drop') %>%
  mutate(source = 'final_US')

base.hhs_kids.ethnicity <- base.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  group_by(time, ethnicity) %>%
  summarise(n = n(), .groups = 'drop') %>%
  mutate(source = 'baseline')

combined <- rbind(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
combined$ethnicity <- factor(combined$ethnicity)

ggplot(combined, aes(x = time, y = n, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')

rm(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
```

```{r}
calculate_hh_proportions <- function(data, group.var) {
  # Step 1: Filter for households with children
  households_with_kids <- data %>%
    filter(nkids > 0) %>%
    select(hidp, time, hh_income, .data[[group.var]]) %>%
    distinct()

  # Step 3: Count households within each income group per year
  household_counts <- households_with_kids %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(count = n(), .groups = 'drop')

  # Step 5: Calculate proportion of households in each group per year
  household_proportions <- household_counts %>%
    left_join(total_households_per_year, by = "time") %>%
    mutate(proportion = count / total_count) %>%
    select(time, .data[[group.var]], proportion)

raw.hh_kids_prop <- calculate_hh_proportions(raw.dat, group.var = 'ethnicity')
base.hh_kids_prop <- calculate_hh_proportions(base.dat, group.var = 'ethnicity')

combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
combined$ethnicity <- factor(combined$ethnicity)

ggplot(combined, aes(x = time, y = proportion, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_col() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')

rm(raw.hh_kids_prop, base.hh_kids_prop, combined)
```

@@

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")

handover_boxplots(raw.dat, base.dat, 'hh_income_diff')
handover_lineplots(raw.dat, base.dat, "hh_income_diff")
# handover_boxplots(raw.dat, base.dat, 'council_tax')
# handover_lineplots(raw.dat, base.dat, "council_tax")

handover_boxplots(base.dat, base.dat, 'hh_income_diff')
handover_lineplots(base.dat, base.dat, "hh_income_diff")
```

@@

#### Absolute
```{r}
# raw.2010 <- raw.dat %>%
#   filter(time == 2010)
# 
# abs.threshold <- weighted.median(x = raw.2010$hh_income, 
#                                  w = raw.2010$weight, 
#                                  na.rm = TRUE)
# abs.threshold <- abs.threshold * 0.6
# 
# print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
```

### Analysis by Quintile

```{r}
density_plot_quintile <- function(raw, base, quintile) {

  raw <- raw %>%
    filter(income_quint == quintile) %>%
    select(pidp, time, hh_income) %>%
    rename(Final_US = hh_income)
  base <- base %>%
    filter(income_quint == quintile) %>%
    select(pidp, time, hh_income) %>%
    rename(Baseline = hh_income)

  #combined <- merge(base, int, by = c('pidp', 'time'))

  combined <- rbind(raw, base)

  combined <- combined %>%
    pivot_longer(cols = Final_US:Baseline,
                 names_to = 'Source',
                 values_to = 'hh_income')

  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
    geom_density_ridges(alpha = 0.3) +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))

  return(p)
}

# density_plot_quintile(base.dat, int.dat, quintile = 1)
# density_plot_quintile(base.dat, int.dat, quintile = 2)
# density_plot_quintile(base.dat, int.dat, quintile = 3)
# density_plot_quintile(base.dat, int.dat, quintile = 4)
# density_plot_quintile(base.dat, int.dat, quintile = 5)
```

#### Mean Income

```{r}
mean_income_quintile <- function(raw, base) {
  raw <- raw %>%
    select(pidp, time, hh_income, income_quint, weight) %>%
    mutate(source = 'Final_US')
  base <- base %>%
    select(pidp, time, hh_income, income_quint, weight) %>%
    mutate(source = 'Baseline')

  combined <- rbind(base, int)

  combined <- combined %>%
    group_by(time, income_quint, source) %>%
    summarise(mean = weighted.mean(hh_income, weight),
              median = weighted.median(hh_income, weight))

  combined$income_quint <- factor(combined$income_quint)
  combined$source <- factor(combined$source)

  p1 <- ggplot(combined, aes(x = time, y = mean, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Mean hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  p2 <- ggplot(combined, aes(x = time, y = median, group = interaction(income_quint, source), color = income_quint, linetype = source, fill = income_quint)) +
    geom_line() +
    labs(title = 'Median hh_income by quintile',
         subtitle = 'Baseline vs Intervention')

  print(p1)
  print(p2)
  #return(p)
}

#mean_income_quintile(base.dat, int.dat)
```

#### Thresholds Over Time

```{r}
# get min-max by group as this is upper and lower limits of the quintiles

# base <- base.dat %>%
#   group_by(time, income_quint) %>%
#   summarise(min = min(hh_income),
#             max = max(hh_income)) %>%
#   mutate(source = 'Baseline')
# int <- int.dat %>%
#   group_by(time, income_quint) %>%
#   summarise(min = min(hh_income),
#             max = max(hh_income)) %>%
#   mutate(source = 'Intervention')
# 
# combined <- rbind(base, int)
# combined$income_quint <- factor(combined$income_quint)
# 
# quintile_threshold_plot <- function(data, year) {
#   ggplot(filter(data, time == year), 
#          aes(x = income_quint, y = min,
#              ymin = min, lower = min, ymax = max, upper = max,
#              group = source, 
#              colour = source, 
#              fill = source)) +
#     geom_crossbar(position = position_dodge()) +
#     labs(title = 'Quintile Thresholds',
#          subtitle = year)
# }
# 
# quintile_threshold_plot(combined, year = 2020)
# quintile_threshold_plot(combined, year = 2021)
# quintile_threshold_plot(combined, year = 2025)
# quintile_threshold_plot(combined, year = 2030)
# quintile_threshold_plot(combined, year = 2035)
```

@@

```{r}
# raw.sf12 <- raw.dat %>%
#   select(pidp, age, time, SF_12, SF_12_diff)
# base.sf12 <- base.dat %>%
#   select(pidp, age, time, SF_12, SF_12_diff)
# 
# sf12.spag <- rbind(raw.sf12, base.sf12)
# 
# sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
# spaghetti_plot(sf12.spag.sample, 'SF_12',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
#                save = shall.we.save,
#                save.path = save.path)
# 
# spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
#                save = shall.we.save,
#                save.path = save.path)
#   
# density_ridges(sf12.spag, "SF_12", 
#                save = T, 
#                save.path = save.path)
# 
# rm(raw.sf12, base.sf12, sf12.spag)
```

@@

@@

```{r}
raw.hh_unique <- raw.dat %>%
  select(hidp, time, nkids, weight) %>%
  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
  mutate(scen = 'final_US')

base.hh_unique <- base.dat %>%
  select(hidp, time, nkids, weight) %>%
  distinct(hidp, time, nkids, .keep_all = TRUE) %>%
  mutate(scen = 'baseline')

#handover_boxplots(raw.hh_unique, base.hh_unique, 'nkids')
handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, nkids)
# base.s <- base.dat %>%
#   select(pidp, age, time, nkids)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## CHILD POVERTY VARS

### Relative poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'relative_poverty')

tit <- 'Relative Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = relative_poverty, colour = relative_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=relative_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'relative_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Absolute Poverty

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'absolute_poverty')

tit <- 'Absolute Poverty'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = absolute_poverty, colour = absolute_poverty)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=absolute_poverty)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'absolute_poverty.png',
         plot = last_plot(),
         path = save.path)
}

### Persistent Poverty

```{r}
# prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'persistent_poverty')
# 
# var <- prepped.list$var
# norm <- prepped.list$norm
# 
# tit <- 'Persistent Poverty'
# 
# # Now plot
# ggplot(data = var, mapping = aes(x = time, y = n, group = persistent_poverty, colour = persistent_poverty)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = tit, subtitle = 'Counts by Level') +
#   xlab('Year') +
#   ylab('Count')
# 
# ggplot(data = norm, mapping = aes(x = time, y = prct, fill=persistent_poverty)) +
#   geom_bar(stat = 'identity') +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = tit) +
#   xlab('Year') +
#   ylab('Proportion')
# 
# if (shall.we.save) {
#   ggsave(filename = 'persistent_poverty.png',
#          plot = last_plot(),
#          path = save.path)
# }
# 
# 
# rm(prepped.list, var, norm, tit)

### Low Income and Material Deprivation

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'low_income_matdep_child')

tit <- 'Material Deprivation Child'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = low_income_matdep_child, colour = low_income_matdep_child)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=low_income_matdep_child)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'low_income_matdep_child.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, var, norm, tit)

@@

```{r}
# handover_boxplots(raw.dat, base.dat, 'hourly_wage')
# handover_lineplots(raw.dat, base.dat, 'hourly_wage')
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, hourly_wage)
# base.s <- base.dat %>%
#   select(pidp, age, time, hourly_wage)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# # now a version limited to 0-100
# spag <- spag %>%
#   filter(hourly_wage <= 300)
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

>>>>

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```

@@

@@

```{r}
raw.maxAge <- raw.dat %>%
  group_by(time) %>%
  summarise(max_age = max(age))

base.maxAge <- base.dat %>%
  group_by(time) %>%
  summarise(max_age = max(age))

handover_lineplots(raw.maxAge, base.maxAge, 'max_age')

@@

```{r}
raw.alive <- raw.dat %>%
  group_by(time) %>%
  summarise(n = n())

base.alive <- base.dat %>%
  group_by(time) %>%
  summarise(n = n())

#handover_boxplots(raw.alive, base.alive, 'n')
handover_lineplots(raw.alive, base.alive, "n")

@@

```{r}
# Step 1: Filter for households with children
households_with_kids <- raw.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time, hh_income) %>%
  distinct() %>%
  select(-hidp)

# Step 2: Calculate income quintiles
households_with_kids <- households_with_kids %>%
  group_by(time) %>%
  mutate(income_quintile = ntile(hh_income, 5)) %>%
  ungroup()

# Step 3: Count households within each income quintile per year
household_count_by_income_quintile <- households_with_kids %>%
  group_by(time, income_quintile) %>%
  summarise(n = n())

household_count_by_income_quintile
```

@@

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
handover_boxplots(raw.dat, base.dat, 'council_tax')
handover_lineplots(raw.dat, base.dat, "council_tax")
```

@@

#### Absolute
```{r}
raw.2010 <- raw.dat %>%
  filter(time == 2010)

abs.threshold <- weighted.median(x = raw.2010$hh_income, 
                                 w = raw.2010$weight, 
                                 na.rm = TRUE)
abs.threshold <- abs.threshold * 0.6

print(sprintf("The absolute poverty threshold is £%.02f", abs.threshold))
```

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

sf12.spag <- rbind(raw.sf12, base.sf12)

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```

@@

## ncigs

```{r}
handover_boxplots(raw.dat, base.dat, 'ncigs')
handover_lineplots(raw.dat, base.dat, "ncigs")
raw.ncigs <- raw.dat %>%
  select(pidp, age, time, ncigs)
base.ncigs <- base.dat %>%
  select(pidp, age, time, ncigs)
ncigs.spag <- rbind(raw.ncigs, base.ncigs)
shall.we.save <- F
pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/10, replace=FALSE)
ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
spaghetti_plot(ncigs.spag.sample, 'ncigs',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
               save = shall.we.save,
               save.path = save.path)

zip_density_ridges(ncigs.spag, "ncigs", 
               save = shall.we.save, 
               save.path = save.path)
rm(raw.ncigs, base.ncigs, ncigs.spag)
```

## ncigs non-zero

raw.ncigs <- raw.dat %>%
  filter(ncigs>0) %>%
  select(pidp, age, time, ncigs)
base.ncigs <- base.dat %>%
  filter(ncigs>0) %>%
  select(pidp, age, time, ncigs)

ncigs.spag <- rbind(raw.ncigs, base.ncigs) # get all smokers.
shall.we.save <- F
pidp_sample <- sample(unique(ncigs.spag$pidp), size=nrow(raw.dat)/100, replace=FALSE)
ncigs.spag.sample <- ncigs.spag[which(ncigs.spag$pidp %in% pidp_sample), ]
spaghetti_plot(ncigs.spag.sample, 'ncigs',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(ncigs.spag.sample, 'ncigs',
               save = shall.we.save,
               save.path = save.path)

zip_density_ridges(ncigs.spag, "ncigs", 
               save = shall.we.save, 
               save.path = save.path)
rm(raw.ncigs, base.ncigs, ncigs.spag)
```

@@

```{r}
raw.hh_unique <- raw.dat %>%
  select(hidp, time, nkids) %>%
  distinct()

base.hh_unique <- base.dat %>%
  select(hidp, time, nkids) %>%
  distinct()

#handover_boxplots(raw.hh_unique, base.hh_unique, 'nkids')
handover_lineplots(raw.hh_unique, base.hh_unique, 'nkids')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, nkids)
base.s <- base.dat %>%
  select(pidp, age, time, nkids)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nkids',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nkids_ind',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
handover_boxplots(raw.dat, base.dat, 'hourly_wage')
handover_lineplots(raw.dat, base.dat, 'hourly_wage')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, hourly_wage)
base.s <- base.dat %>%
  select(pidp, age, time, hourly_wage)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

# now a version limited to 0-100
spag <- spag %>%
  filter(hourly_wage <= 300)
spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```
